% =============================================================================
% CHAPTER 1: INTRODUCTION
% =============================================================================

\chapter{Introduction}

\section{Background}

This is the introduction chapter of your thesis. Each chapter begins on a new page as required by the format guidelines. The text should be justified and use 1.5 line spacing.

Every paragraph should have at least three sentences and develop one main idea with a clear topic sentence that expresses this idea.

\section{Problem Statement}

Describe the problem that your research addresses. This section should clearly articulate the gap in knowledge or the issue that needs to be resolved.

\section{Research Objectives}

\subsection{Main Objective}

State your main research objective here.

\subsection{Specific Objectives}

\begin{enumerate}
    \item First specific objective
    \item Second specific objective  
    \item Third specific objective
\end{enumerate}

\section{Research Questions}

List your research questions here:

\begin{enumerate}
    \item What is the main research question?
    \item What are the supporting questions?
\end{enumerate}

\section{Significance of the Study}

Explain why your research is important and what contribution it will make to the field.

\section{Scope and Limitations}

Define the boundaries of your study and acknowledge any limitations.

\section{Organization of the Thesis}

Provide a brief overview of how the thesis is organized:

Chapter 1 provides an introduction to the research...

Chapter 2 reviews relevant literature...

Chapter 3 describes the research methodology...

And so on for each chapter.
