% =============================================================================
% CHAPTER 3: METHODOLOGY
% =============================================================================

\chapter{Research Methodology}

\section{Introduction}

This chapter describes the research methodology employed in this study.

\section{Research Design}

Describe your research design (e.g., qualitative, quantitative, mixed methods).

As shown in equation~\ref{eq:reward}, the reward function penalizes crashes heavily.

\begin{equation}
\label{eq:reward}
r_t =
\begin{cases}
\phantom{-}1 & \text{if } s_t \in S_{\text{success}} \\
\phantom{-}0 & \text{if } s_t \in S_{\text{sloped}} \\
-10 & \text{if } s_t \in S_{\text{crash}} \\
-1 & \text{if } s_t \in S_{\text{trunc}} \cup S_{\text{bounds}} \\
-0.1 & \text{otherwise}
\end{cases}
\end{equation}



\section{Study Area}

Describe your study area if applicable.

\section{Data Collection Methods}

\subsection{Primary Data}

Describe how you collected primary data.

\subsection{Secondary Data}

Describe any secondary data sources used.

\section{Sampling}

\subsection{Sample Size}

Explain how you determined your sample size.

\subsection{Sampling Technique}

Describe the sampling technique used.

\section{Data Analysis}

Describe the methods used to analyze your data.

\section{Ethical Considerations}

Discuss any ethical issues and how they were addressed.

\section{Limitations}

Acknowledge any methodological limitations.

\section{Chapter Summary}

Summarize the methodology described in this chapter.
